\bf The usage of bootstrap method in shape-restricted regression

### 2023-09-11 Manuscript/manuscript.tex
Add files via upload

In table ~\ref{Table1}, \(x\) represents the certain time point we selected in the domain of the function, and \(f(x)\) is its true value calculated by the certain known function. CP represents coverage percentage of pointwise confidence interval we built by the bootstrap methods under certain degrees of freedom. We can see that in all those functions and degrees of freedom we have given, the bootstrap method gives pointwise confidence intervals coverage that are closed to the nominal level \(95\%\). And we can also see that while n gets larger, the result of \(n = 1000\), which can be seen in Table ~\ref{Table2} is much better than \(n = 100\) in each same level of degrees of freedom. We can also see that in some situations, for example, when df = 10, some empirical coverage rate is as low as 0.3 to 0.4, this may due to the degrees of freedom is not suitable for this data regression, which might cause some problems. We can also see that via Figure ~\ref{Figure1} when degrees of freedom equals to 10, the curve is not that smooth compare to the curve of degrees of freedom 6, and in some situations, its shape is not even closed to the true function. So we can see that degree of freedom is a crucial variable and different degrees of freedom will impact the result of CP of the confidence interval. It should be cautious to choose when we are using the splines regression since it will influence the result of the inference a lot. However, since it is not the main scope of this paper, we will not concern a lot about how to choose the best model to enhence the CP result. Overall, we can see that those pointwise confidence intervals made by bootstrap method works fine in suitable degrees of freedom, and in the rest of this article we will use a real world shape-restricted data to give out an data analysis with the bootstrap method.

>>>>

In table ~\ref{Table1}, \(x\) represents the certain time point we selected in the domain of the function, and \(f(x)\) is its true value calculated by the certain known function. CP represents coverage percentage of pointwise confidence interval we built by the bootstrap methods under certain degrees of freedom. We can see that in all those functions and degrees of freedom we have given, the bootstrap method gives pointwise confidence intervals coverage that are closed to the nominal level \(95\%\). And we can also see that while n gets larger, the result of \(n = 1000\), which can be seen in Table ~\ref{Table2} is much better than \(n = 100\) in each same level of degrees of freedom. We can also see that in some situations, for example, when df = 10, some empirical coverage rate is as low as 0.3 to 0.4, this may due to the degrees of freedom is not suitable for this data regression, which might cause some problems. We can also see that via Figure ~\ref{fig:DataAndRegressions} when degrees of freedom equals to 10, the curve is not that smooth compare to the curve of degrees of freedom 6, and in some situations, its shape is not even closed to the true function. So we can see that degree of freedom is a crucial variable and different degrees of freedom will impact the result of CP of the confidence interval. It should be cautious to choose when we are using the splines regression since it will influence the result of the inference a lot. However, since it is not the main scope of this paper, we will not concern a lot about how to choose the best model to enhance the CP result. Overall, we can see that those pointwise confidence intervals made by bootstrap method works fine in suitable degrees of freedom, and in the rest of this article we will use a real world shape-restricted data to give out an data analysis with the bootstrap method.
